Limits to Ecological Forecasting: Estimating Uncertainty for Critical Transitions with Deep Learning

### 2022-09-22 manuscript/manuscript.Rmd
Changing word choice in caption

```{r figure6}
#| fig.cap="CRPS scores over time for each scenario.
#|  Each line represents the CRPS scores against a replicate of time series observations from the 'true model'. 
#|  The general pattern across these plots is that forecast skill gets worse over time -- gradually 
#|  in the case of a Hopf bifurcation or suddenly in response to the saddle-node bifurcation. 
#|  In the stochastic transition case,  the scores tend to diverge in two branches, where high values indicate periods of 
#|  time when the forecast predicts the wrong equilibrium state and the lower branch indicates predictions of the correct one. The time axis in this plot and in Figure 7 refers to the time from the beginning of the forecast window, not the time from the beginning of the time series as in other plots."

@@

```{r figure7}
#| fig.cap="Logs skill score over time. 
#|  Forecasts which underestimate uncertainty do substantially worse in logs score than in CRPS score. 
#|  Comparing this panel to those in Figure 6 highlights scenarios that most often underestimate uncertainty. 
#|  Generally, MCMC performs better relative to other models under this metric than it does under CRPS, 
#|  reflecting the bias-variance tradeoff taken when using biased estimators in machine learning.
#|  The time axis in this plot and in Figure 6 refers to the time from the beginning of the forecast window, not the time from the beginning of the time series as in other plots."

>>>>

```{r figure6}
#| fig.cap="CRPS scores over time for each scenario.
#|  Each line represents the CRPS scores against a replicate of time series observations from the 'true model'. 
#|  The general pattern across these plots is that forecast skill gets worse over time -- gradually 
#|  in the case of a Hopf bifurcation or suddenly in response to the saddle-node bifurcation. 
#|  In the stochastic transition case,  the scores tend to diverge in two branches, where high values indicate periods of 
#|  time when the forecast predicts the wrong equilibrium state and the lower branch indicates predictions of the correct one. The time axis in this plot and in Figure 7 refers to the time from the beginning of the forecast horizon, not the time from the beginning of the time series as in other plots."

@@

```{r figure7}
#| fig.cap="Logs skill score over time. 
#|  Forecasts which underestimate uncertainty do substantially worse in logs score than in CRPS score. 
#|  Comparing this panel to those in Figure 6 highlights scenarios that most often underestimate uncertainty. 
#|  Generally, MCMC performs better relative to other models under this metric than it does under CRPS, 
#|  reflecting the bias-variance tradeoff taken when using biased estimators in machine learning.
#|  The time axis in this plot and in Figure 6 refers to the time from the beginning of the forecast horizon, not the time from the beginning of the time series as in other plots."
